---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DoSimPFI2011

<!-- badges: start -->
<!-- badges: end -->

The goal of DoSimPFI2011 is to reproduce simulation section in Parametric fractional imputation for missing data analysis (Kim, [2011](https://doi.org/10.1093/biomet/asq073)).

## Installation

You can install the development version of DoSimPFI2011 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tspark422/DoSimPFI2011")
```

## Usage

You can change parameters in the simulation if they are compatible. For example, beta can be any vector if it is two-dimensional. However, what this function provides remains unchanged as the simulation. That is, $\eta_{1} = \mathit{E} \left( Y_{1} \right)$, $\eta_{2} = \mathit{E} \left( Y_{2} \right)$, $\eta_{3} = \beta_{1}$, and $\eta_{4} = pr\left( y_{1} < 3 \right)$.  
This is a basic example which shows you how to reproduce the simulation: Use fractional imputation method with the original simulation setting.

```{r example}
library(DoSimPFI2011)
## Original Simulation setting
n=200; beta=c(1, 0.7); sigma=1; phi=c(-3, 0.5, 0.7)
suppressWarnings({ 
 # result with fractional imputation method (method='FI')
 res_FI <- sim2011(n=n, beta=beta, sigma=sigma, phi=phi, M=100, max.iter=50, eps=1e-09, B=20, method='FI')
 
 # Obtain point estimator of eta1, variance of eta1 under incomplete data, variance of eta1 under complete data
 point_estimator_eta1 <- colMeans(res_FI$eta1)
 point_estimator_eta1
})
```
This is another example using calibration fractional imputation method with changed beta
```{r example2}
library(DoSimPFI2011)
## Change beta from (1, 0.7) to (2, 0.3)
n=200; beta=c(2, 0.3); sigma=1; phi=c(-3, 0.5, 0.7)
suppressWarnings({ 
 # result with calibration fractional imputation method (method='CFI')
 res_CFI <- sim2011(n=n, beta=beta, sigma=sigma, phi=phi, M=5, max.iter=50, eps=1e-09, B=20, method='CFI')
 
 # Obtain point estimator of eta2, variance of eta2 under incomplete data, variance of eta2 under complete data
 point_estimator_eta2 <- colMeans(res_CFI$eta2)
 point_estimator_eta2
})
```
